Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-12 lineages_18Q3.Rmd
updated rmd

Filter for point mutations:
```{r}
crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1)
test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
```

@@

>>>>

Filter for point mutations:
```{r}
crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1)
test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
test_ptmuts <- filter(crispr_data_ptmuts, Hugo_Symbol == "KRAS")
```

@@

```{r}
compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts[which(crispr_data_ptmuts$Hugo_Symbol == "KRAS"),], method = "wilcox.test", p.adjust.method = "BH")
```
